Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-03-17 manuscript/manuscript.tex

\title{3D Magnetic modelling of ellipsoidal bodies}

@@

Table \ref{tab:parameters-warrego} shows the parameters defining
a synthetic orebody which is based on that presented by
\citet{farrar1979} to represent the Warrego orebody.
Figure \ref{fig:tfa-warrego} shows the total-field anomaly
$\Delta T (\mathbf{r})$ (Eq. \ref{eq:delta-T-approx}) produced
by the synthetic body on a regular grid of $100 \times 100$
points at a constant vertical coordinate $z = 0$ \unit{m}.
The total-field anomaly varies from $\approx -295.3$ \unit{nT}
to $\approx 149.5$ \unit{nT}, resulting in a peak-to-peak amplitude
of $\approx 444.9$ \unit{nT}, and was calculated by using the 
true magnetization $\mathbf{M}$ defined in Eqs. 
\ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}.

@@

As expected, the differences calculated by using the higher isotropic
susceptibility (Fig. \ref{fig:tfa-differences-warrego}a) are very large.
The peak-to-peak amplitude is $\approx 212.0$ \unit{nT}
and represents $\approx 48 \%$ of the peak-to-peak amplitude of
the total-field anomaly shown in Fig. \ref{fig:tfa-warrego}.
This result reinforces that the use of the approximated magnetization
$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) may negatively impact
the magnetic modelling of bodies with high isotropic susceptibility.

Figure \ref{fig:tfa-differences-warrego}b shows the differences calculated
by using $\chi_{1} = 0.1$ \unit{SI}.
It is commonly accepted that, for bodies having isotropic susceptibilities
lower than or equal to $0.1$ \unit{SI}, the self-demagnetization can be neglected and,
consequently, the magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
is a good approximation of the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
In our test, the use of $\chi_{1} = 0.1$ \unit{SI} leads to a relative error
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 4.2 \%$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
The peak-to-peak amplitude of the differences in the total-field anomaly
(Fig. \ref{fig:tfa-differences-warrego}b) is $\approx 1.5$ \unit{nT},
which represents $\approx 4.5 \%$ of the peak-to-peak amplitude of the
total-field anomaly calculates by using the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).

Finally, Fig. \ref{fig:tfa-differences-warrego}c shows the differences
calculated by using $\chi_{2} = 0.116$ \unit{SI}.
This value was calculated by using Eq. \ref{eq:chi-max} with a
target relative error $\epsilon = 8 \%$ and the $\tilde{n}^{\dagger}_{max}$
defined by Eq. \ref{eq:n-tilde-dagger-33-triaxial}.
By using this isotropic susceptibility, it is expected that the
calculated relative error 
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization be
lower than or equal to the target relative error $\epsilon = 8 \%$.
In this test, the use of $\chi_{2} = 0.116$ \unit{SI} leads to a relative error
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 4.9 \%$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
The peak-to-peak amplitude of the differences in the total-field anomaly
(Fig. \ref{fig:tfa-differences-warrego}c) is $\approx 2.0$ \unit{nT},
which represents $\approx 5.1 \%$ of the peak-to-peak amplitude of the
total-field anomaly calculates by using the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
In this case, the use an isotropic susceptibility greater than the usual
limit $0.1$ \unit{SI} does not mislead the magnetic modelling
dramatically. On the contrary, it shows small discrepancies in the
magnetic modelling and validates Eq. \ref{eq:chi-max}.

>>>>

\title{Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies}

@@

Table \ref{tab:parameters-warrego} shows the parameters defining
a synthetic orebody which is based on that presented by
\citet{farrar1979} to represent the Warrego orebody.
Figure \ref{fig:tfa-warrego} shows the total-field anomaly
$\Delta T (\mathbf{r})$ (Eq. \ref{eq:delta-T-approx}) produced
by the synthetic body on a regular grid of $100 \times 100$
points at a constant vertical coordinate $z = 0$ \unit{m}.
The total-field anomaly varies from $\approx -176$ \unit{nT}
to $\approx 237$ \unit{nT}, resulting in a peak-to-peak amplitude
of $\approx 413$ \unit{nT}, and was calculated by using the 
true magnetization $\mathbf{M}$ defined in Eqs. 
\ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}.

@@

As expected, the differences calculated by using the higher isotropic
susceptibility (Fig. \ref{fig:tfa-differences-warrego}a) are very large.
The peak-to-peak amplitude is $\approx 141$ \unit{nT}
and represents $\approx 34 \%$ of the peak-to-peak amplitude of
the total-field anomaly shown in Fig. \ref{fig:tfa-warrego}.
This result reinforces that the use of the approximated magnetization
$\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx}) may negatively impact
the magnetic modelling of bodies with high isotropic susceptibility.

Figure \ref{fig:tfa-differences-warrego}b shows the differences calculated
by using $\chi_{1} = 0.1$ \unit{SI}.
It is commonly accepted that, for bodies having isotropic susceptibilities
lower than or equal to $0.1$ \unit{SI}, the self-demagnetization can be neglected and,
consequently, the magnetization $\breve{\mathbf{M}}$ (Eq. \ref{eq:M-approx})
is a good approximation of the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
In our test, the use of $\chi_{1} = 0.1$ \unit{SI} leads to a relative error
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 2.4 \%$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
The peak-to-peak amplitude of the differences in the total-field anomaly
(Fig. \ref{fig:tfa-differences-warrego}b) is $\approx 0.8$ \unit{nT},
which represents $\approx 2.9 \%$ of the peak-to-peak amplitude of the
total-field anomaly calculates by using the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).

Finally, Fig. \ref{fig:tfa-differences-warrego}c shows the differences
calculated by using $\chi_{2} = 0.116$ \unit{SI}.
This value was calculated by using Eq. \ref{eq:chi-max} with a
target relative error $\epsilon = 8 \%$ and the $\tilde{n}^{\dagger}_{max}$
defined by Eq. \ref{eq:n-tilde-dagger-33-triaxial}.
By using this isotropic susceptibility, it is expected that the
calculated relative error 
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1}$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization be
lower than or equal to the target relative error $\epsilon = 8 \%$.
In this test, the use of $\chi_{2} = 0.116$ \unit{SI} leads to a relative error
$\| \delta \mathbf{M} \| \, \| \mathbf{M} \|^{-1} \approx 2.8 \%$
(Eq. \ref{eq:perturbed-M-inequality}) in the magnetization.
The peak-to-peak amplitude of the differences in the total-field anomaly
(Fig. \ref{fig:tfa-differences-warrego}c) is $\approx 1.1$ \unit{nT},
which represents $\approx 3.3 \%$ of the peak-to-peak amplitude of the
total-field anomaly calculates by using the true magnetization $\mathbf{M}$
(Eqs. \ref{eq:M-K-isotropic} and \ref{eq:M-K-isotropic-inverse-Lambda}).
In this case, the use an isotropic susceptibility greater than the usual
limit $0.1$ \unit{SI} does not mislead the magnetic modelling
dramatically. On the contrary, it shows small discrepancies in the
magnetic modelling and validates Eq. \ref{eq:chi-max}.
